Scalar on Function Regression

### 2022-01-05 Presentation/slides.tex
Update slides.tex

	\begin{frame}{Introduction}
		Jona \\	
		\begin{itemize}
			\item Near-infrared (NIR) spectroscopy enables fast diagnostics by using the NIR region of the electromagnetic spectrum
			\item Suited for field-monitoring / on-line analysis and diagnostics of e.g: prediction of octane ratings!

@@

		Motivation from multivariate regression (multivariate dgp).

		\begin{itemize}
			\item
			A simple functional dataset is given by $x_{n}(t_{j,n}) \in \mathbb{R}, t_{j,n} \in [T_1, T_2], n = 1,2,...,N, j = 1,2,..., J_n  $
			\item Continuous underlying process, where $x_n(t)$ exists at any point $t$, but is only observed at $x_{n}(t_{j,n})$
			\item NIR-spectroscopy measurements, financial data, medical data, human perception (musical pitch, ...)

@@

    		$Y_{1,f} = NIR \times f + \mathcal{N}(0,1) \times var(NIR \times f)/0.9 - var(NIR \times f)$, \\
    		  $Y_{2,f} = NIR \times f + \mathcal{N}(0,1) \times var(NIR \times f)/0.9 - var(NIR \times f)$ be two responses for $f \in f_1, f_2$.		
    		 	\item
    		 	 Four combinations with different number of cubic basis-function $n_{basis} \in (5,6,...,25)$ to perform regression using basis expansion and the FPCR approach.
			\item Compare results via criteria (CV, Mallows CP,...)
			\item 
			{\color{green} add results here!}

@@

	\begin{frame}{Simulation Setup \& Application cont.}
		\begin{itemize}
		\item
    		Use insights from the simulation study to uncover dependence.
    		\item
    		Same setup, but without generated curves.
    		\item
    		Validation set approach:	Scores of testdata needs to be estimated by the trainingdata.  {\color{green} explain in detail?}
    		\item
    		Report results by MSE scaled by variance.
		\end{itemize}
	\end{frame}

>>>>

	\begin{frame}{Introduction}

		\begin{itemize}
			\item Near-infrared (NIR) spectroscopy enables fast diagnostics by using the NIR region of the electromagnetic spectrum
			\item Suited for field-monitoring / on-line analysis and diagnostics of e.g: prediction of octane ratings!

@@

		\begin{itemize}
			\item
			A simple functional dataset is given by $x_{n}(t_{j,n}) \in \mathbb{R}, t_{j,n} \in [T_1, T_2], n = 1,2,...,N, j = 1,2,..., J_n  $
			\item Continuous underlying process, where $x_n(t)$ exists at any point $t$, but is only observed at $x_{n}(t_{j,n})$, eg.: growth curves, financial data, human perception (music pitch,...).

@@

    		$Y_{1,f} = \mathbf{NIR \times f}  + \mathcal{N}(0,1) \times var(NIR \times f)/0.9 - var(NIR \times f)$, \\
    		  $Y_{2,f} = \mathbf{NIR \times f} + \mathcal{N}(0,1) \times var(NIR \times f)/0.9 - var(NIR \times f)$ be two responses for $f \in f_1, f_2$.		
    		 	\item
    		 	 Four combinations with different number of cubic basis-function $n_{basis} \in (5,6,...,25)$ to perform regression using basis expansion and the FPCR approach.
			\item Compare results via criteria (CV, Mallows CP,...)
			\item 
			{\color{green} add results here!}

@@

	\begin{frame}{Simulation Setup \& Application cont.}
		\begin{itemize}
		\item
    		Use insights from the simulation study to uncover dependence.
    		\item
    		Similar setup, but using only bsplie basis expansion and initial 60 spectral curves.
    		\item
    		Validation set approach:	Scores of testdata needs to be estimated by the trainingdata.  {\color{green} explain in detail?}
    		\item
    		Report results by MSE scaled by variance.
		\end{itemize}
	\end{frame}
